Quantifying unmet ICU beds in tertiary hospitals in urban India using Propensity

### 2022-09-23 manuscript.Rmd
main efter revidering

@@

A diverse mix of public, for-profit and not-for-profit private actors provide health services in India. According to a WHO 2022 report, India has 76 709 non-ventilator supported and 39 476 ventilator-supported ICU beds @ICUbeds. This is 8.2 per 100 000 inhabitants.
The WHO report also highlight the probable shortage of ICU resources in India, though in the context of the COVID-19 pandemic.

>>>>

<!-- 
FYI: utmanat volymkraven, de är motstridiga med kravet "Innehåller endast sådan information som är nödvändig för att förstå och motivera studiens syfte och metodik i stort"
-->

@@

A diverse mix of public, for-profit and not-for-profit private actors provide health services in India. According to a WHO 2022 report, India has 76 709 non-ventilator supported and 39 476 ventilator-supported ICU beds @ICUbeds. This is 8.2 per 100 000 inhabitants.
This same report also highlight the probable shortage of ICU resources in India, though in the context of the COVID-19 pandemic.
